---
title: "Food Preferences from around the world"
output: html_notebook
---

I would consider myself somewhat of a foodie, nothing gets me in a good mood like a well made meal. I'm pretty sure that I'm not alone. Now this got me thinking, about how each country has their own type of food. Would this mean that people in different countries would have different likes and dislikes?

Of course this would be the case, now the only question is what kind of preferences exist.

# Importing libraries

```{r}
library(tidyverse)
```

# Getting our data

For this data viz project I will be taking a look at a Kaggle data set call [Food Preferences](https://www.kaggle.com/vijayashreer/food-preferences). The data was collected via survey that was conducted among participants from different countries and demographics.

```{r}
data <- read_csv('Food_Preference.csv')
head(data)
```

```{r}
summary(data)
```

# Cleaning our data

Looking at our data we seem only to have missing values in regards to gender.

```{r echo=FALSE}
unique(data$Gender)
```

This could be due to not in fact wanting to disclose their gender so we can change the "NA" to "Not disclosed" without any issues.

```{r echo=FALSE}
data$Gender[is.na(data$Gender)] <- "Not disclosed"
unique(data$Gender)
```

Another detail to take into account seems to be Nationality. There are multiple instances of the same nationality just in different forms. As well as a mystery nationality called "**MY**" that doesn't seem to be an abbreviation of any known nation.

```{r echo=FALSE}
unique(data$Nationality)
```

The easiest solution I found was to find all the repeating nationalities and replace them with a single one.

```{r include=FALSE}
data$Nationality[data$Nationality == 'Indonesia'] <- 'Indonesian'
data$Nationality[data$Nationality == 'Pakistan'] <- 'Pakistani'
data$Nationality[data$Nationality == 'Malaysia' | data$Nationality == 'MALAYSIAN'] <- 'Malaysian'
```

```{r echo=FALSE}
unique(data$Nationality)
```

# Data overview

Let's get a sense of what we are dealing with. Starting with the food:

```{r echo=FALSE}
ggplot(data = data) +
  geom_bar(mapping = aes(Food), fill=rgb(0.5,0.6,0.1,0.7), width=0.3) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  coord_flip()
```
