---
title: "Food Preferences from around the world"
output: html_notebook
---

I would consider myself somewhat of a foodie, nothing gets me in a good mood like a well made meal. I'm pretty sure that I'm not alone. Now this got me thinking, about how each country has their own type of food. Would this mean that people in different countries would have different likes and dislikes?

Of course this would be the case, now the only question is what kind of preferences exist.

# Importing libraries

```{r}
library(tidyverse)
library(corrgram)
library(fastDummies)
library(GGally)
```

# Getting our data

For this data viz project I will be taking a look at a Kaggle data set call [Food Preferences](https://www.kaggle.com/vijayashreer/food-preferences). The data was collected via survey that was conducted among participants from different countries and demographics.

```{r}
data <- read_csv('Food_Preference.csv')
head(data)
```

```{r}
summary(data)
```

# Cleaning our data

Looking at our data we seem only to have missing values in regards to gender.

```{r echo=FALSE}
unique(data$Gender)
```

This could be due to not in fact wanting to disclose their gender so we can change the "NA" to "Not disclosed" without any issues.

```{r echo=FALSE}
data$Gender[is.na(data$Gender)] <- "Not disclosed"
unique(data$Gender)
```

Another detail to take into account seems to be Nationality. There are multiple instances of the same nationality just in different forms. As well as a mystery nationality called "**MY**" that doesn't seem to be an abbreviation of any known nation (For the purposes of this project it will count as Malaysian).

```{r echo=FALSE}
unique(data$Nationality)
```

The easiest solution I found was to find all the repeating nationalities and replace them with a single one.

```{r include=FALSE}
data$Nationality[data$Nationality == 'Indonesia'] <- 'Indonesian'
data$Nationality[data$Nationality == 'Pakistan'] <- 'Pakistani'
data$Nationality[data$Nationality == 'Malaysia' | data$Nationality == 'MALAYSIAN'] <- 'Malaysian'
data$Nationality[data$Nationality == 'MY'] <- 'Malaysian'
```

```{r echo=FALSE}
unique(data$Nationality)
```

# Data Analysis

```{r echo=FALSE}
ggplot(data = data) +
  geom_bar(mapping = aes(Food, fill = Gender), width=0.4, alpha = 0.8) +
  theme(axis.text.y = element_text(angle = 50, vjust = 1, hjust = 1),
        axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_fill_brewer(palette = "RdYlGn") +
  coord_flip()
```

Here we can see that there is a much larger preference for traditional food, also an interesting thing to note though is that males tend to prefer Western food while females lean more towards traditional food.

Why is this? According to an article publish by the [National Center for Biotechnology Information](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2531152/): "A growing body of evidence suggests that the food choices a mother makes during her pregnancy may set the stage for an infant's later acceptance of solid foods."

It's my belief that due to women preferring more traditional food, a very likely scenario is that during pregnancy they would be more likely to consume traditional food which would be a contributing factor that leads into the offspring preferring traditional food, and the cycle would continue.

```{r echo=FALSE}
ggplot(data, aes(Food, Age)) +
  geom_boxplot(color="red", fill="red", alpha=0.4, 
               notch=TRUE, notchwidth = 0.8,
               outlier.colour="orange", outlier.fill="orange", outlier.size=3,
               width = 0.1) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank())
```

The older one seems to get, the more they prefer traditional food. In general though overall traditional food is enjoyed by all ages, whereas Western Food is enjoyed mostly by young adults.

```{r include=FALSE}
corrData = dummy_cols(data[, -c(1,2,3,4)],remove_first_dummy = F)
```

```{r echo=FALSE}
ggcorr(
  corrData,
  name = expression(rho),
  max_size = 20,
  min_size = 15,
  size = 3,
  hjust = 0.75,
  nbreaks = 6,
  angle = -35,
  palette = "PuOr")
```

# Conclusion

We know that there is a larger preference for traditional food.